\subsection{Technologies used}


The package \NOTE{algorithm2e} allows you write nearly all imaginable code structures as pseudo code in LaTex. A referece of commands can be found here: \url{http://www.cs.toronto.edu/~frank/Useful/algorithm2e.pdf}. Do not forget to wrap the pseudo code into a figure, thus it will be included into list of figures.\\

The following example demonstrates the package with a bubble sort algorithm. Note, that the directive \NOTE{repeat - until} is the same as the \NOTE{do-while} directive.


\newpage
\subsection{GPU, Local machine}

Writing mathematical equations can be a very important part of your work. This applies especially, if you want to analyze and evaluate your gathered data. The following example shows a calculation of Kohen's Cappa, a measurement which represents the inter coder reliability in coding qualitative data.\\

Let's assume the following results of coding a text by two different persons:


Continuing from this basis, the calculation can be proceeded with Cohen's Kappa defined as


\subsection{TACC, Stampede2, job submission process}

Sometimes you want to include text which include characters that could trigger commands. At this point it useful to wrap them into the \NOTE{verbatim} environment. The text is uninterpreted and listet as is.

\scriptsize
\begin{verbatim}
2015_5_13/23-19-33:550: ************* LOG INFO  *************
2015_5_13/23-19-33:550: name: user1
2015_5_13/23-19-33:550: [0]: 534
2015_5_13/23-19-33:550: [1]: 321
2015_5_13/23-19-33:550: [2]: 094832
2015_5_13/23-19-33:550: [3]: 3980429804
\end{verbatim}
\normalsize	

code


\small
\begin{lstlisting}[keywordstyle=\color{blue},language=Python]
<!-- an XML comment -->
<entry type="normal" pattern="a" />
<entry type="normal" pattern="b" />
<entry type="formula" pattern="t=a+b+c" required="1"/>
\end{lstlisting}
\normalsize	